Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-25 paper/snakemajoranas.tex
go over todos

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
% The Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are more than an order of magnitude better for the zigzag system, even though these are plotted for the optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.  % From phase diagram figure
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.

>>>>

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
The improvements occur regardless of any particular parameter values, moreover, even when using the parameter values of the optimal gap in the straight system (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.
